Summary

### 2015-10-15 inst/examples/summary.Rmd
publication places ok

```{r city2, echo=FALSE, message=FALSE, warning=FALSE}
f <- "output.tables/publicationplaces.csv"
print(paste("Complete counts in file:", f))
write.table(cbind(Place = names(tab), Documents = tab), file = f, sep = "|", quote = F, row.names = F)
```

>>>>

```{r city2, echo=FALSE, message=FALSE, warning=FALSE}
f <- "output.tables/publication_place.csv"
print(paste("Complete counts in file:", f))
tmp <- write_xtable(df$publication_place, filename = f)
```
